---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
Reading the unzipped data using read.csv
```{r }
activity <- read.csv("activity.csv")

#activity$date <- as.POSIXct(activity$date, "%Y-%m-%d")
#weekday <- weekdays(activity$date)
#activity <- cbind(activity,weekday)
totalStepsPerDay <- tapply(activity$steps,activity$date,sum,na.rm=TRUE)
hist(totalStepsPerDay,main="Total Steps Per Day Histogram",xlab="steps",col = "red",breaks = seq(0,25000, by=2500),ylim=c(0,20))
```

## What is mean total number of steps taken per day?

```{r }
median(totalStepsPerDay)
mean(totalStepsPerDay)
#tapply(activity$steps,activity$date,mean,na.rm=TRUE)
#tapply(activity$steps,activity$date,median,na.rm=TRUE)

```

## What is the average daily activity pattern?
averageStepsPerDay <- tapply(activity$steps,activity$date,mean,na.rm=TRUE)
averageStepsPerDay <- averageStepsPerDay[!is.na(averageStepsPerDay)]
plot(as.Date(names(averageStepsPerDay)),averageStepsPerDay,xlab="Date",ylab="Average Steps Per Day",type="l")
which.max(averageStepsPerDay)

## Imputing missing values
To inputing missing values, first I identify the NA


## Are there differences in activity patterns between weekdays and weekends?
